On the Bit Complexity of Finding Points in Connected Components of a Smooth Real Hypersurface

### 2020-02-03 main.tex
Updated Section 6

% test 
\usepackage{mathrsfs}
\usepackage{bm}
% new commands and shortcuts
\def\td{{\bf todo}}
\def\bs{\textit{\textbf{s}}}
\def\Lb{\textit{\textbf{L}}}
\def\Xb{\textit{\textbf{X}}}
\def\Lambdab{\bm{\Lambda}}
\def\Thetab{\bm{\Theta}}
\def\thetab{\bm{\vartheta}}
\def\xb{\textit{\textbf{x}}}
\def\fb{\textit{\textbf{f}}}
\def\ab{\textit{\textbf{a}}}
\def\pb{\textit{\textbf{p}}}
\def\ajb{\overline{a_j}}
\def\bjb{\overline{b_{j,l}}}
\def\pjb{\overline{P_{j}}}
\DeclareMathOperator{\GL}{GL}
\DeclareMathOperator{\htt}{ht}
\def\C{\mathbb{C}}
\def\vt{\vartheta}
\def\Q{\mathbb{Q}}
\def\R{\mathbb{R}}
\def\rs{\mathscr{R}}
\def\P{\mathscr{P}}
\def\d{\delta}
\def\sing{ \textrm{sing}}
\def\codim{ \textrm{codim}}
\def\jac{ \textrm{jac}}
\def\exp{\textrm{exp}}
\def\grad{\textrm{grad}}
\def\rank{\textrm{rank}}
\def\reg{\textrm{reg}}
\def\jt{\widetilde{J}}
\def\At{\widetilde{A}}
\def\Yt{\widetilde{Y}}
\def\dt{s}
%% \def\dt{\widetilde{d}}
\def\Dt{\widetilde{D}}
\def\rk{\textrm{rank }}
\def\pa{\partial}
\def\D{\Delta}
\def\Z{\frak{Z}}
\def\I{\frak{I}}
\def\Is{\frak{I}^{\star}}
\def\A{\frak{A}}
\def\fp{\frak{P}}
\def\sp{\mathscr{P}}
\def\la{\langle}
\def\ra{\rangle}
% matrices 
\def\bbm{\begin{bmatrix}}
\def\ebm{\end{bmatrix}}
%%
%% \BibTeX command to typeset BibTeX logo in the docs
\AtBeginDocument{%
  \providecommand\BibTeX{{%
    \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}}

@@

We will let $\Phi$ be a mapping essentiall equal to 

@@

so that 

@@

\Phi_A^{-1}(0)= W(\pi_i,V^A).

@@

We want to apply Theorem 5.1, and thus we show that $0$ is a regular value of $\Phi$, where then it follows that $\Delta_1 \subset \C^{n^2}$ exists with the property that if $A \in \C^{n^2}-\Delta_1$ then $0$ is a regular value of $\Phi_A,$ which means that 
\jac_{\xb}(\Phi_A) = \jac_{\xb}\left(f^A(x),\frac{\pa f^A(x)}{\pa X_{i+1}},\hdots,\frac{\pa f^A(x)}{\pa X_n}\right)
has full rank for all $\xb \in V(f^A)$. Then, by the Jacobian criterion \cite[Theorem 16.19]{ECA}, $f^A$ satisfies $\textbf{H}_i^{'}(1),\textbf{H}_i^{'}(2)$ and $\textbf{H}_i^{'}(3)$.

@@

0 is a regular value of $\Phi$.

@@

Let $A_1,\hdots,A_n$ denote the columns of $A,$ and let $(\xb,A) \in \C^n \times \C^{n^2}$ be such that \[
f^A(\xb) = \frac{\partial f^A(\xb)}{\partial X_{i+1}}=\hdots= \frac{\partial f^A(\xb)}{\partial X_n}=0.

@@

We want to show that the system

@@

f(Ax),(\grad(f)\cdot 
A_{i+1})(Ax),\hdots, 
(\grad(f)\cdot 
A_n)(Ax)

@@

defines a radical ideal of dimension ? whose variety is smooth, which holds if and only if 
f,\grad(f)\cdot 
A_{i+1},\hdots, 
\grad(f)\cdot 
A_n
defines a radical ideal of dimension ? whose variety is smooth. Now, let $\Phi$ be the mapping

@@

    \Phi: \C^n \times \C^{n^2} &\rightarrow \C^{n-i+1} \\

@@

For all $(\xb,A) \in \Phi^{-1}(0),$ the Jacobian matrix of $\Phi$ at $(\xb,A)$ has full rank $n-i+1$. Indeed, set 

@@

Since $\deg \Phi \leq D,$ it follows by Theorem 5.1 that a hypersurface $\Delta_1 \subset \C^{n^2}$ exists, of degree at most $\td$ with the property that, if $A \in \C^{n^2}-\Delta_1,$ then $0$ is a regular value of $\Phi_{A}$, which means that 

@@

\jac_\textit{\textbf{x}} \Phi_A &=\left(f(\xb),\grad(f(\xb))\cdot A_{i+1},\hdots. \grad(f(\xb))\cdot A_{n} \right) 
has full rank for all $\xb \in V(f^A)$ ($\cap \R^n$?). It follows that 

@@

also has full rank for all $\xb \in V(f^A)$ ($\cap \R^n$?). Therefore, for each $i \in \{1,\hdots,n\},$ by the Jacobian criterion \cite[Theorem 16.19]{ECA}, $f^A$ satisfies $\textbf{H}_i^{'}(1),\textbf{H}_i^{'}(2)$ and $\textbf{H}_i^{'}(3)$.%

>>>>

% test 
\usepackage{mathrsfs}
\usepackage{bm}
% new commands and shortcuts
\def\td{{\bf todo}}
\def\bs{\textit{\textbf{s}}}
\def\bz{\textit{\textbf{0}}}
\def\Lb{\textit{\textbf{L}}}
\def\Xb{\textit{\textbf{X}}}
\def\Lambdab{\bm{\Lambda}}
\def\Thetab{\bm{\Theta}}
\def\thetab{\bm{\vartheta}}
\def\xb{\textit{\textbf{x}}}
\def\fb{\textit{\textbf{f}}}
\def\ab{\textit{\textbf{a}}}
\def\pb{\textit{\textbf{p}}}
\def\ajb{\overline{a_j}}
\def\bjb{\overline{b_{j,l}}}
\def\pjb{\overline{P_{j}}}
\DeclareMathOperator{\GL}{GL}
\DeclareMathOperator{\htt}{ht}
\def\C{\mathbb{C}}
\def\vt{\vartheta}
\def\Q{\mathbb{Q}}
\def\R{\mathbb{R}}
\def\rs{\mathscr{R}}
\def\P{\mathscr{P}}
\def\d{\delta}
\def\sing{ \textrm{sing}}
\def\codim{ \textrm{codim}}
\def\jac{ \textrm{jac}}
\def\exp{\textrm{exp}}
\def\grad{\textrm{grad}}
\def\rank{\textrm{rank}}
\def\reg{\textrm{reg}}
\def\jt{\widetilde{J}}
\def\At{\widetilde{A}}
\def\Yt{\widetilde{Y}}
\def\dt{s}
%% \def\dt{\widetilde{d}}
\def\Dt{\widetilde{D}}
\def\rk{\textrm{rank }}
\def\pa{\partial}
\def\D{\Delta}
\def\Z{\frak{Z}}
\def\I{\frak{I}}
\def\Is{\frak{I}^{\star}}
\def\A{\frak{A}}
\def\fp{\frak{P}}
\def\sp{\mathscr{P}}
\def\la{\langle}
\def\ra{\rangle}
% matrices 
\def\bbm{\begin{bmatrix}}
\def\ebm{\end{bmatrix}}
%%
%% \BibTeX command to typeset BibTeX logo in the docs
\AtBeginDocument{%
  \providecommand\BibTeX{{%
    \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}}

@@

Let $\Phi$ be the polynomiall mapping 

@@

so that $\Phi_A^{-1}(0)= W(\pi_i,V^A).$ We want to apply Theorem 5.1, and thus we show that $0$ is a regular value of $\Phi$, where then it follows that $\Delta_1 \subset \C^{n^2}$ exists with the property that if $A \in \C^{n^2}-\Delta_1$ then  

@@

\jac_{\xb}(\Phi_A) = \jac_{\xb}\left(f^A(\xb),\frac{\pa f^A(\xb)}{\pa X_{i+1}},\hdots,\frac{\pa f^A(\xb)}{\pa X_n}\right)

@@

has full rank at all $\xb \in V(f^A)$. Then, by the Jacobian criterion \cite[Theorem 16.19]{ECA}, $f^A$ satisfies $\textbf{H}_i^{'}(1),\textbf{H}_i^{'}(2)$ and $\textbf{H}_i^{'}(3)$.

@@

$\bz$ is a regular value of $\Phi$.

@@

Let $A_1,\hdots,A_n$ denote the columns of $A,$ and let $(\xb,A) \in \C^n \times \C^{n^2}$ be such that 
$f^A(\xb) = \frac{\partial f^A(\xb)}{\partial X_{i+1}}=\hdots= \frac{\partial f^A(\xb)}{\partial X_n}=\bz.$
We want to show that the system of polynomials 
f(Ax),(\grad(f)\cdot A_{i+1})(Ax),\hdots, (\grad(f)\cdot A_n)(Ax)

@@

defines a radical ideal of dimension ? whose variety is smooth (we just want the Jacobian of the system to have full rank?), which holds if and only if 

@@

f,\grad(f)\cdot A_{i+1},\hdots, \grad(f)\cdot A_n

@@

defines a radical ideal of dimension ? whose variety is smooth. Let $\Psi$ be the mapping

@@

    \Psi: \C^n \times \C^{n^2} &\rightarrow \C^{n-i+1} \\

@@

For all $(\xb,A) \in \Psi^{-1}(0),$ the Jacobian matrix of $\Psi$ at $(\xb,A)$ has full rank $n-i+1$. Indeed, set 

@@

Since $\deg \Phi \leq D,$ it follows by Theorem 5.1 that a hypersurface $\Delta_1 \subset \C^{n^2}$ exists, of degree at most $\td$ with the property that, if $A \in \C^{n^2}-\Delta_1,$ then 

@@

@@

has full rank for all $\xb \in V(f^A)$ ($\cap \R^n$?). Therefore, for each $i \in \{1,\hdots,n\},$ by the Jacobian criterion \cite[Theorem 16.19]{ECA}, $f^A$ satisfies $\textbf{H}_i^{'}(1),\textbf{H}_i^{'}(2)$ and $\textbf{H}_i^{'}(3)$.%
